A Bioconductor workflow for processing and analysing spatial proteomics data

### 2018-04-17 bioc-workflow-resubmit.tex
more changes to pre-processing section; should now also build on travis

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData: none
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: X X.1 ... Cell.Surface.Proteins (25 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
##  MSnbase version: 2.4.2
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

will list the 62 datasets that are
available in \Biocexptpkg{pRolocdata}.

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlstd{MSnbase}\hlopt{::}\hlkwd{combine}\hlstd{(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r2)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 6725 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2Y3-3 (6725 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Tue Apr 17 08:39:23 2018 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{filterNA}\hlstd{(combined)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Tue Apr 17 08:39:23 2018 
## Subset [6725,20][5032,20] Tue Apr 17 08:39:24 2018 
## Removed features with more than 0 NAs: Tue Apr 17 08:39:24 2018 
## Dropped featureData's levels Tue Apr 17 08:39:24 2018 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{prots} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"Q8CG48"}\hlstd{,} \hlstr{"Q8CG47"}\hlstd{,} \hlstr{"Q8K2Z4"}\hlstd{,} \hlstr{"Q8C156"}\hlstd{)}
\hlstd{foi13s} \hlkwb{<-} \hlkwd{FeaturesOfInterest}\hlstd{(}\hlkwc{description} \hlstd{=} \hlstr{"13S consensin proteins"}\hlstd{,}
                             \hlkwc{fnames} \hlstd{= prots,}
                             \hlkwc{object} \hlstd{= hl)}
\hlstd{foi13s}
\end{alltt}
\begin{verbatim}
## Traceable object of class "FeaturesOfInterest"
##  Created on Tue Apr 17 08:39:26 2018 
##  Description:
##   13S consensin proteins
##  4 features of interest:
##    Q8CG48, Q8CG47, Q8K2Z4, Q8C156
\end{verbatim}
\begin{alltt}
\hlkwd{plot2D}\hlstd{(hl)}
\hlkwd{addLegend}\hlstd{(hl,} \hlkwc{cex} \hlstd{=} \hlnum{.6}\hlstd{)}
\hlkwd{highlightOnPlot}\hlstd{(hl, foi13s)}
\end{alltt}
\end{kframe}
\includegraphics[width=.8\textwidth]{figure/foi-1}

@@

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Tue Apr 17 08:39:26 2018
\begin{table}[ht]
\centering
\begin{tabular}{rrllr}
  \hline
 & Replicate & Tag & Gradient.Fraction & Iodixonal.Density \\ 
  \hline
X127C &   1 & 127C & 8 to 9 (pooled) & 11.00 \\ 
  X127C.1 &   2 & 127C & 7 to 9 (pooled) & 10.00 \\ 
   \hline
\end{tabular}
\caption{Differences in gradient fraction pooling.} 
\label{tab:pdtab}
\end{table}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126 X127N ... X131.1 (20 total)
##   varLabels: Replicate Tag Gradient.Fraction Iodixonal.Density
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: uniprot.accession uniprot.id ... pd (27 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Added markers from  'mrk' marker vector. Tue Apr 17 08:39:25 2018 
## Added markers from  'pdres' marker vector. Tue Apr 17 08:39:26 2018 
##  MSnbase version: 2.4.2
\end{verbatim}
\begin{alltt}
\hlkwd{getMarkers}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"pd"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## organelleMarkers
##                          40S Ribosome 
##                                   106 
##                          60S Ribosome 
##                                    95 
## Endoplasmic reticulum/Golgi apparatus 
##                                   393 
##                         Mitochondrion 
##                                   525 
##                           Phenotype 1 
##                                   300 
##                           Phenotype 2 
##                                   253 
##                           Phenotype 3 
##                                   203 
##                           Phenotype 4 
##                                    74 
##                           Phenotype 5 
##                                    91 
##                       Plasma membrane 
##                                   421 
##                            Proteasome 
##                                    92 
##                               unknown 
##                                  2479
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{(ts} \hlkwb{<-} \hlkwd{orgQuants}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{=} \hlnum{.5}\hlstd{))}
\end{alltt}
\begin{verbatim}
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4363460               0.3023446               0.3833708 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6846500               0.5947855               0.4246911 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4302963               0.5753825               0.9498381 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7947918               0.7075039               0.3176585 
##         Plasma membrane              Proteasome 
##               0.7124225               0.4149409
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4363460               0.3023446               0.3833708 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6846500               0.5947855               0.4246911 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4302963               0.5753825               0.9498381 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7947918               0.7075039               0.3176585 
##         Plasma membrane              Proteasome 
##               0.7124225               0.4149409
\end{verbatim}
\begin{alltt}
\hlstd{hl} \hlkwb{<-} \hlkwd{getPredictions}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{= ts)}
\end{alltt}
\begin{verbatim}
## ans
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##                      86                     170                      84 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##                     296                     474                      95 
##    Extracellular matrix                Lysosome           Mitochondrion 
##                      28                     123                     523 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##                     230                     344                      39 
##         Plasma membrane              Proteasome                 unknown 
##                     326                     157                    2057
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

## R version 3.4.4 Patched (2018-03-19 r74516)

@@

## [1] stats4    parallel  methods   stats     graphics  grDevices utils    
## [8] datasets  base     

@@

##  [1] pRolocdata_1.16.0    pRoloc_1.18.0        MLInterfaces_1.58.1 
##  [4] cluster_2.0.7-1      annotate_1.56.2      XML_3.98-1.10       
##  [7] AnnotationDbi_1.40.0 IRanges_2.12.0       S4Vectors_0.16.0    
## [10] MSnbase_2.4.2        ProtGenerics_1.10.0  BiocParallel_1.12.0 
## [13] mzR_2.12.0           Rcpp_0.12.16         Biobase_2.38.0      
## [16] BiocGenerics_0.24.0  xtable_1.8-2         BiocStyle_2.6.1     

@@

##   [4] lazyeval_0.2.1        splines_3.4.4         ggvis_0.4.3          

@@

##  [10] foreach_1.4.4         BiocInstaller_1.28.0  htmltools_0.3.6      

@@

##  [19] limma_3.34.9          recipes_0.1.2         gower_0.1.2          

@@

##  [28] dplyr_0.7.4           RCurl_1.95-4.10       hexbin_1.27.2        
##  [31] genefilter_1.60.0     bindr_0.1.1           impute_1.52.0        

@@

##  [40] zlibbioc_1.24.0       kernlab_0.9-25        ddalpha_1.3.2        
##  [43] prabclus_2.2-6        DEoptimR_1.0-8        abind_1.4-5          
##  [46] scales_0.5.0.9000     vsn_3.46.0            mvtnorm_1.0-7        
##  [49] DBI_0.8               viridisLite_0.3.0     progress_1.1.2       
##  [52] magic_1.5-8           foreign_0.8-69        bit_1.1-12           
##  [55] proxy_0.4-22          mclust_5.4            preprocessCore_1.40.0
##  [58] lava_1.6.1            prodlim_1.6.1         sampling_2.8         
##  [61] htmlwidgets_1.0       httr_1.3.1            threejs_0.3.1        
##  [64] FNN_1.1               RColorBrewer_1.1-2    fpc_2.1-11           
##  [67] modeltools_0.2-21     pkgconfig_2.0.1       flexmix_2.3-14       
##  [70] nnet_7.3-12           caret_6.0-79          tidyselect_0.2.4     
##  [73] rlang_0.2.0           reshape2_1.4.3        munsell_0.4.3        
##  [76] mlbench_2.1-1         tools_3.4.4           msdata_0.18.0        
##  [79] RSQLite_2.1.0         pls_2.6-0             broom_0.4.4          
##  [82] evaluate_0.10.1       geometry_0.3-6        stringr_1.3.0        
##  [85] mzID_1.16.0           yaml_2.1.18           ModelMetrics_1.1.0   
##  [88] bit64_0.9-7           robustbase_0.92-8     randomForest_4.6-14  
##  [91] purrr_0.2.4           dendextend_1.7.0      bindrcpp_0.2.2       
##  [94] nlme_3.1-137          whisker_0.3-2         mime_0.5             
##  [97] RcppRoll_0.2.2        biomaRt_2.34.2        compiler_3.4.4       
## [100] e1071_1.6-8          
##  [ reached getOption("max.print") -- omitted 37 entries ]

>>>>

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData: none
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: X X.1 ... Cell.Surface.Proteins (25 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
##  MSnbase version: 2.5.12
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

will list the 75 datasets that are
available in \Biocexptpkg{pRolocdata}.

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{combine}\hlstd{(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r2)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 6725 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2Y3-3 (6725 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
##   pubMedIds: 26754106 
## Annotation:  
## - - - Processing information - - -
## Combined [5489,10] and [6268,10] MSnSets Tue Apr 17 11:44:16 2018 
##  MSnbase version: 2.5.9
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{filterNA}\hlstd{(combined)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
##   pubMedIds: 26754106 
## Annotation:  
## - - - Processing information - - -
## Combined [5489,10] and [6268,10] MSnSets Tue Apr 17 11:44:16 2018 
## Subset [6725,20][5032,20] Tue Apr 17 11:44:17 2018 
## Removed features with more than 0 NAs: Tue Apr 17 11:44:17 2018 
## Dropped featureData's levels Tue Apr 17 11:44:17 2018 
##  MSnbase version: 2.5.9
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{prots} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"Q8CG48"}\hlstd{,} \hlstr{"Q8CG47"}\hlstd{,} \hlstr{"Q8K2Z4"}\hlstd{,} \hlstr{"Q8C156"}\hlstd{)}
\hlstd{foi13s} \hlkwb{<-} \hlkwd{FeaturesOfInterest}\hlstd{(}\hlkwc{description} \hlstd{=} \hlstr{"13S consensin proteins"}\hlstd{,}
                             \hlkwc{fnames} \hlstd{= prots,}
                             \hlkwc{object} \hlstd{= hl)}
\hlstd{foi13s}
\end{alltt}
\begin{verbatim}
## Traceable object of class "FeaturesOfInterest"
##  Created on Tue Apr 17 11:44:19 2018 
##  Description:
##   13S consensin proteins
##  4 features of interest:
##    Q8CG48, Q8CG47, Q8K2Z4, Q8C156
\end{verbatim}
\begin{alltt}
\hlkwd{plot2D}\hlstd{(hl)}
\hlkwd{addLegend}\hlstd{(hl,} \hlkwc{cex} \hlstd{=} \hlnum{.6}\hlstd{)}
\hlkwd{highlightOnPlot}\hlstd{(hl, foi13s)}
\end{alltt}
\end{kframe}
\includegraphics[width=.8\textwidth]{figure/foi-1}

@@

% latex table generated in R 3.6.0 by xtable 1.8-2 package
% Tue Apr 17 11:44:19 2018
\begin{table}[ht]
\centering
\begin{tabular}{rrllr}
  \hline
 & Replicate & Tag & Gradient.Fraction & Iodixonal.Density \\ 
  \hline
X127C &   1 & 127C & 8 to 9 (pooled) & 11.00 \\ 
  X127C.1 &   2 & 127C & 7 to 9 (pooled) & 10.00 \\ 
   \hline
\end{tabular}
\caption{Differences in gradient fraction pooling.} 
\label{tab:pdtab}
\end{table}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126 X127N ... X131.1 (20 total)
##   varLabels: Replicate Tag Gradient.Fraction Iodixonal.Density
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: uniprot.accession uniprot.id ... pd (27 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Added markers from  'mrk' marker vector. Tue Apr 17 11:44:18 2018 
## Added markers from  'pdres' marker vector. Tue Apr 17 11:44:19 2018 
##  MSnbase version: 2.5.12
\end{verbatim}
\begin{alltt}
\hlkwd{getMarkers}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"pd"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## organelleMarkers
##                          40S Ribosome 
##                                   106 
##                          60S Ribosome 
##                                    95 
## Endoplasmic reticulum/Golgi apparatus 
##                                   393 
##                         Mitochondrion 
##                                   525 
##                           Phenotype 1 
##                                   300 
##                           Phenotype 2 
##                                   253 
##                           Phenotype 3 
##                                   203 
##                           Phenotype 4 
##                                    74 
##                           Phenotype 5 
##                                    91 
##                       Plasma membrane 
##                                   421 
##                            Proteasome 
##                                    92 
##                               unknown 
##                                  2479
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{(ts} \hlkwb{<-} \hlkwd{orgQuants}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{=} \hlnum{.5}\hlstd{))}
\end{alltt}
\begin{verbatim}
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4368645               0.3031282               0.3889317 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6760609               0.6075289               0.4353435 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4221860               0.5895546               0.9499026 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7952921               0.7096399               0.3106030 
##         Plasma membrane              Proteasome 
##               0.7232975               0.4205260
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4368645               0.3031282               0.3889317 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6760609               0.6075289               0.4353435 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4221860               0.5895546               0.9499026 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7952921               0.7096399               0.3106030 
##         Plasma membrane              Proteasome 
##               0.7232975               0.4205260
\end{verbatim}
\begin{alltt}
\hlstd{hl} \hlkwb{<-} \hlkwd{getPredictions}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{= ts)}
\end{alltt}
\begin{verbatim}
## ans
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##                      85                     171                      89 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##                     299                     477                      99 
##    Extracellular matrix                Lysosome           Mitochondrion 
##                      27                     123                     521 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##                     230                     343                      38 
##         Plasma membrane              Proteasome                 unknown 
##                     317                     156                    2057
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

## R Under development (unstable) (2018-04-02 r74505)

@@

## [1] stats4    parallel  stats     graphics  grDevices utils     datasets 
## [8] methods   base     

@@

##  [1] pRolocdata_1.17.3    pRoloc_1.19.4        MLInterfaces_1.59.1 
##  [4] cluster_2.0.7        annotate_1.57.3      XML_3.98-1.10       
##  [7] AnnotationDbi_1.41.4 IRanges_2.13.28      S4Vectors_0.17.41   
## [10] MSnbase_2.5.12       ProtGenerics_1.11.0  BiocParallel_1.13.3 
## [13] mzR_2.13.6           Rcpp_0.12.16         Biobase_2.39.2      
## [16] BiocGenerics_0.25.3  xtable_1.8-2         BiocStyle_2.7.8     

@@

##   [4] lazyeval_0.2.1        splines_3.6.0         ggvis_0.4.3          

@@

##  [10] foreach_1.4.4         BiocInstaller_1.29.6  htmltools_0.3.6      

@@

##  [19] limma_3.35.14         recipes_0.1.2         gower_0.1.2          

@@

##  [28] dplyr_0.7.4.9003      RCurl_1.95-4.10       hexbin_1.27.2        
##  [31] genefilter_1.61.1     bindr_0.1.1           impute_1.53.0        

@@

##  [40] zlibbioc_1.25.0       kernlab_0.9-25        ddalpha_1.3.1.1      
##  [43] prabclus_2.2-6        DEoptimR_1.0-8        scales_0.5.0         
##  [46] vsn_3.47.1            mvtnorm_1.0-7         DBI_0.8              
##  [49] viridisLite_0.3.0     progress_1.1.2        foreign_0.8-70       
##  [52] bit_1.1-12            proxy_0.4-22          mclust_5.4           
##  [55] preprocessCore_1.41.0 lava_1.6.1            prodlim_1.6.1        
##  [58] sampling_2.8          htmlwidgets_1.0       httr_1.3.1           
##  [61] threejs_0.3.1         FNN_1.1               RColorBrewer_1.1-2   
##  [64] fpc_2.1-11            modeltools_0.2-21     pkgconfig_2.0.1      
##  [67] flexmix_2.3-14        nnet_7.3-12           caret_6.0-78         
##  [70] tidyselect_0.2.4      rlang_0.2.0           reshape2_1.4.3       
##  [73] munsell_0.4.3         mlbench_2.1-1         tools_3.6.0          
##  [76] msdata_0.19.3         RSQLite_2.1.0         pls_2.6-0            
##  [79] broom_0.4.4           evaluate_0.10.1       stringr_1.3.0        
##  [82] mzID_1.17.0           yaml_2.1.18           ModelMetrics_1.1.0   
##  [85] bit64_0.9-7           robustbase_0.92-8     randomForest_4.6-14  
##  [88] purrr_0.2.4           dendextend_1.7.0      bindrcpp_0.2.2.9000  
##  [91] nlme_3.1-136          whisker_0.3-2         mime_0.5             
##  [94] RcppRoll_0.2.2        biomaRt_2.35.13       compiler_3.6.0       
##  [97] e1071_1.6-8           affyio_1.49.2         tibble_1.4.2         
## [100] stringi_1.1.7        
##  [ reached getOption("max.print") -- omitted 33 entries ]
